plackett_luce_monster

### 2022-07-13 inst/plackett_luce_monster.Rmd
typo

Above, we see from the function body that he reported `RB,BB,C,T,W`
three times[first row], `BB,RB,T,C,W` twice [second row], and so on;
perhaps his ranking depends on the weather or how tired he is on any
given day.  Observe that in almost every case he ranks `RB` and `BB`
consecutively.  Function `RB_BB_LF()` takes argument `s` that
quantifies the perceived similarity between `RB` and `BB`.  For
example:

>>>>

Above, we see from the function body that he reported `RB,BB,C,T,W`
three times [first row], `BB,RB,T,C,W` twice [second row], and so on;
perhaps his ranking depends on the weather or how tired he is on any
given day.  Observe that in almost every case he ranks `RB` and `BB`
consecutively.  Function `RB_BB_LF()` takes argument `s` that
quantifies the perceived similarity between `RB` and `BB`.  For
example:
